Reducing Acceptance Marks in Emerson-Lei Automata by QBF Solving

### 2023-03-19 paper/main.tex
s/TELA automaton/TELA/

\paragraph*{Related results}
There is a simple technique~\cite{babiak.13.spin} reducing the number
of acceptance marks in \emph{transition-based generalised Büchi
  automata (TGBA)} without changing its structure. We are not aware
of any existing research aimed at simplification of acceptance
formulas of TELA or reduction of the number of its acceptance marks
without increasing the number of states. There exists only a SAT-based
approach that transforms a deterministic TELA automaton to an
equivalent automaton with a given acceptance condition and a given
number of states~\cite{baarir.15.lpar} (if such an automaton
exists). Further, there are some SAT-based approaches aimed to reduce
the number of states of automata over infinite words. More preceisely,
there are reductions designed for nondeterministic Büchi
automata~\cite{ehlers.10.spin}, deterministic Büchi
automata~\cite{ehlers.10.sat}, and deterministic generalized Büchi
automata~\cite{baarir.14.forte}. Note that these techniques are
usually very slow and their authors typically suggest to use them only
for specific purposes like looking for cases where some automata
construction can be improved.

@@

This section explains how we use the QBF formulas constructed in the
previous section to reduce the number of acceptance marks in TELA
automata. First, we describe a \emph{single-level} reduction, which
uses only a single kind of QBF formulas. More precisely, we talk about
\emph{level~1}, \emph{level~2}, or \emph{level~3} reduction when
$\Phi_{1,C,K}$, $\Phi_{2,C,K}$, or
$\Phi_{3,C,K}$ is used, respectively.

>>>>

\paragraph*{Related results}
There is a simple technique~\cite{babiak.13.spin} reducing the number
of acceptance marks in \emph{transition-based generalised Büchi
  automata (TGBA)} without changing its structure. We are not aware
of any existing research aimed at simplification of acceptance
formulas of TELA or reduction of the number of its acceptance marks
without increasing the number of states. There exists only a SAT-based
approach that transforms a deterministic TELA to an
equivalent automaton with a given acceptance condition and a given
number of states~\cite{baarir.15.lpar} (if such an automaton
exists). Further, there are some SAT-based approaches aimed to reduce
the number of states of automata over infinite words. More preceisely,
there are reductions designed for nondeterministic Büchi
automata~\cite{ehlers.10.spin}, deterministic Büchi
automata~\cite{ehlers.10.sat}, and deterministic generalized Büchi
automata~\cite{baarir.14.forte}. Note that these techniques are
usually very slow and their authors typically suggest to use them only
for specific purposes like looking for cases where some automata
construction can be improved.

@@

This section explains how we use the QBF formulas constructed in the
previous section to reduce the number of acceptance marks in TELA.
First, we describe a \emph{single-level} reduction, which
uses only a single kind of QBF formulas. More precisely, we talk about
\emph{level~1}, \emph{level~2}, or \emph{level~3} reduction when
$\Phi_{1,C,K}$, $\Phi_{2,C,K}$, or
$\Phi_{3,C,K}$ is used, respectively.
